My title

### 2024-02-12 paper/paper.qmd
updated qmd/pdf

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Maroosh Gillani
  - Aaron Liu
  - Jimmy Luc
thanks: "Code and data are available at: https://github.com/rex009x/us_birth_rates/tree/master/data . A replication of various aspects in this paper are available at: LINK ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
# workplace setup

@@

```{r graph1, fig.cap="Trend in US Birth Rates from 1980 - 2020", echo=FALSE}

@@

```{r graph2, fig.cap="Trends in Birth Rates by Population Subgroup", echo=FALSE}

#| label: fig-2

@@

```{r graph3, fig.cap="Children Ever Born by Mother’s Age and Birth Cohort", echo=FALSE}

#| label: fig-3

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Maroosh Gillani
  - Aaron Liu
  - Jimmy Luc
thanks: "Code and data are available at: https://github.com/rex009x/us_birth_rates/tree/master/data . A replication of various aspects in this paper are available at: LINK ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
# workplace setup

@@

```{r graph1, fig.cap="Trend in US Birth Rates from 1980 - 2020", echo=FALSE}
#| echo: false
#| message: false
#| warning: false

@@

```{r graph2, fig.cap="Trends in Birth Rates by Population Subgroup", echo=FALSE}
#| echo: false
#| message: false
#| warning: false
#| label: fig-2

@@

```{r graph3, fig.cap="Children Ever Born by Mother’s Age and Birth Cohort", echo=FALSE}
#| echo: false
#| message: false
#| warning: false
#| label: fig-3
